Potential Factors of Decreasing Birth Rates in the US since the Great Recession and Beyond

### 2024-02-09 outputs/paper/paper.qmd
Update paper.qmd

# Introduction
1) broader context to motivate
2) some detail about what the paper is about
3) a clear gap that needs to be filled
4) what was done
5) what was found
6) why it is important
7) the structure of the paper

@@

From now on, every white refers to non-Hispanic, caucassian. Every black refers to non-Hispanic, African American. Hispanic refers to people with Hispanic ethinicity majority from south America. 
# Data {#sec-data}

@@

# map

## Methodology

### Data Cleaning

### Data Modification

### Data Visualization

>>>>

# Introduction
1) broader context to motivate
2) some detail about what the paper is about
3) a clear gap that needs to be filled
4) what was done
5) what was found
6) why it is important - replacement level fertility
7) the structure of the paper - 1. trend in US Birth Rates 2. Trends in Birth Rates by Population Subgroup 2.1 Five-year age group 2.2 Race and ethinicity

@@

From now on, every white refers to non-Hispanic, caucassian. Every black refers to non-Hispanic, African American. Hispanic refers to people with Hispanic ethinicity majority from south America.

# Data {#sec-data}

## Methodology
The data for the trend in US Birth Rates, births per 1,000 women age 15-44 from the period 1980 to 2020 was acquired from CDC Vital Statistics Births Reports for 2015, 2019 and 2020 (Martin and Mathews 2017; Martin and Driscoll 2021; Hamilton and Osterman 2021). Another trends in Birth Rates by Population Subgroup, specifically birth rates by age group, race and ethnicity are again gathered from CDC Vital Statistics Births Reports. Original paper uses single-age population counts, among all races from 1969-2019 and by race and Hispanic origin from 1990-2019, from the CDC SEER database (CDC NCI 2021).

@@

Map
